Toward dynamic models of combat or lack thereof in animal mating

### 2015-12-24 ms.tex
variable table

Within the immature phase, we assume males grow with rate
\begin{equation} \label{eq:growth}
\frac{{\rm d} m}{{\rm d} t} = a \, m^ b
\end{equation}
where $a$ is mass-based rate of growth. Integrating eq. \ref{eq:growth}, the size of individuals at time $t$, having started growing at time $0$ is given by
\begin{equation} \label{eq:growth}
m(t) = \left(m(0)^{1-b} + t a(1-b)\right)^{\frac1{1-b}},
\end{equation}
while the he time $\tau$ taken for a male to grow from $m(0) \rightarrow m$ is then
\begin{equation} \label{eq:tau}
\tau(m_0, m) = \frac1{a(1-b)}\left(m ^{1-b} - m_0 ^{1-b}\right).
\end{equation}

@@

Traits:
\begin{enumerate}
    \item Visible to opponent:
    \begin{enumerate}
        \item Size, influenced by time entered maturity
    \end{enumerate}
    \item invisible to opponent:
    \begin{enumerate}
        \item Energy level, influenced by size and past actions
        \item Abandon Rate, influences RR abandonment rate
        \item Aggressiveness, influences escalation in contests
        \item Encounter Rate, influences chance of being selected for an event
    \end{enumerate}
\end{enumerate}

>>>>

Within the immature phase, we assume males grow with rate
\begin{equation} \label{eq:growth}
\frac{{\rm d} m}{{\rm d} t} = a \, m^ b
\end{equation}
where $a$ is mass-based rate of growth. Integrating eq. \ref{eq:growth}, the size of individuals at time $t$, having started growing at time $0$ is given by
\begin{equation} \label{eq:growth}
m(t) = \left(m(0)^{1-b} + t a(1-b)\right)^{\frac1{1-b}},
\end{equation}
while the time $\tau$ taken for a male to grow from $m(0) \rightarrow m$ is then
\begin{equation} \label{eq:tau}
\tau(m_0, m) = \frac1{a(1-b)}\left(m ^{1-b} - m_0 ^{1-b}\right).
\end{equation}

@@

Traits:
\begin{enumerate}
    \item Visible to opponent:
    \begin{enumerate}
        \item Size, influenced by time entered maturity
    \end{enumerate}
    \item invisible to opponent:
    \begin{enumerate}
        \item Energy level, influenced by size and past actions
        \item Abandon Rate, influences RR abandonment rate
        \item Aggressiveness, influences escalation in contests
        \item Encounter Rate, influences chance of being selected for an event
    \end{enumerate}
\end{enumerate}
\clearpage

I am not sure if this is the way to do this, 
or if there is a way to do it with refs (?)
\begin{table}[h!]
    \caption{Variable names and definitions in the model.}
    \centering
    \begin{tabular}{c | c | l }
        \hline
        Symbol & unit & Description\\
        \hline
        \hline
        $K$ & & number of individual males \\
        $N$ & & number of nests \\
        $R_i$ & & repoductive value of nest of nest $i$\\
        $\bar{R}$ & & average repoductive value of nest\\
        \hline
        $m$ & $kg$ & mass\\
        \hline
    \end{tabular}
\end{table}
